Verification of concurrent design patterns with data

### 2019-04-26 2018-Arch-pNets/Coordination Camera ready/arch-pNets.tex
arch-pNets paper: run a spell-checker

In the general case, the encoding relies on the causal semantics of the
algebra of BIP connectors \cite{BliSif10-causal-fmsd}.  Disregarding
the variables and data transfer, the Algebra of Connectors $\ac(P)$
\cite{BliSif07-acp-emsoft} provides a syntactic notation for the BIP
connectors.  The causal semantics of the connectors, given in terms of
the Algebra of Causal Interaction Trees $\ct(P)$, explicitates the
causal dependencies through an encoding mapping
$\tau: \ac(P) \rightarrow \ct(P)$.  Another mapping $R: \ct(P)
\rightarrow \cru(P)$ encodes causal interaction trees into systems of
causal rules, which are Boolean implications similar to the ones in
the example above.  %% We briefly summarise the key definitions and
%% results in \app{algebras}.
The $\ac(P)$, $\ct(P)$ and $\cru(P)$
representations of the connectors in \fig{schema:ArchFailure:BIP} are
shown in \tab{connectors} (elements shown in red can be removed for
simplification as described in the example above).

>>>>

In the general case, the encoding relies on the causal semantics of the
algebra of BIP connectors \cite{BliSif10-causal-fmsd}.  Disregarding
the variables and data transfer, the Algebra of Connectors $\ac(P)$
\cite{BliSif07-acp-emsoft} provides a syntactic notation for the BIP
connectors.  The causal semantics of the connectors, given in terms of
the Algebra of Causal Interaction Trees $\ct(P)$, elicits the
causal dependencies through an encoding mapping
$\tau: \ac(P) \rightarrow \ct(P)$.  Another mapping $R: \ct(P)
\rightarrow \cru(P)$ encodes causal interaction trees into systems of
causal rules, which are Boolean implications similar to the ones in
the example above.  %% We briefly summarise the key definitions and
%% results in \app{algebras}.
The $\ac(P)$, $\ct(P)$ and $\cru(P)$
representations of the connectors in \fig{schema:ArchFailure:BIP} are
shown in \tab{connectors} (elements shown in red can be removed for
simplification as described in the example above).
